---
title: "Microbial Interactions in infant fecal microcosm"
author: "Oriane Moyne"
date: "5/1/2023"
output: html_document
---


## Load libraries

```{r, message = FALSE}
# Packages I commonly use
library(stringr)
library(ggplot2)
library(FactoMineR)
library(factoextra)
library(reshape)
library(reshape2)
library(data.table)
library(dplyr)
library(gplots)
library(tidyr)
library(vegan)
```

## Data import

```{r}
data <- fread("/home/moyne/Moyne_disk/MOMI_2020/MI04_prebiotics_test/multiomics_batch2_BHI/WoL_subset_NEW/counts_species_uniref.tsv/counts_species_uniref.tsv", 
                    sep="\t", 
                    dec=".", 
                    header = TRUE, 
                    stringsAsFactors = FALSE, 
                    na.strings = "", 
                   check.names = FALSE)

data <- as.data.frame(data)
colnames(data) <- str_replace(colnames(data), "mi04t", "MI04T")
colnames(data)[1] <- "FeatureID"


# Two samples (fru_1 and ref_1) have been swapped in the BHI experiment: See Chloe's lab notebook
colnames(data)[colnames(data) == "MI04T1_fru_1_metaG"] <- "mi04t2_ref_1_metaG"
colnames(data)[colnames(data) == "MI04T2_ref_1_metaG"] <- "mi04t1_fru_1_metaG"

colnames(data)[colnames(data) == "MI04T1_fru_1_metaT"] <- "mi04t2_ref_1_metaT"
colnames(data)[colnames(data) == "MI04T2_ref_1_metaT"] <- "mi04t1_fru_1_metaT"

colnames(data)[colnames(data) == "MI04T1_fru_1_metaRS"] <- "mi04t2_ref_1_metaRS"
colnames(data)[colnames(data) == "MI04T1_fru_2_metaRS"] <- "mi04t2_ref_2_metaRS"
colnames(data)[colnames(data) == "MI04T1_fru_3_metaRS"] <- "mi04t2_ref_3_metaRS"

colnames(data)[colnames(data) == "MI04T2_ref_1_metaRS"] <- "mi04t1_fru_1_metaRS"
colnames(data)[colnames(data) == "MI04T2_ref_2_metaRS"] <- "mi04t1_fru_2_metaRS"
colnames(data)[colnames(data) == "MI04T2_ref_3_metaRS"] <- "mi04t1_fru_3_metaRS"

colnames(data) <- str_replace(colnames(data), "mi04t", "MI04T")
colnames(data) <- str_split(colnames(data), "_wol", simplify = TRUE)[, 1]

# Add columns
data$species <- str_split(data$FeatureID, "\\|", simplify = TRUE)[, 1]
data$uniref <- str_split(data$FeatureID, "\\|", simplify = TRUE)[, 2]

# reorder columns alphabetically 
colnames(data) <- str_replace(colnames(data), "fru", "zfru")
data <- data[, c("FeatureID", "species", "uniref", "Name", sort(colnames(data)[str_detect(colnames(data), "meta")]))]
colnames(data) <- str_replace(colnames(data), "zfru", "fru")

 # keep only data from the tested sample
data <- data[, !str_detect(colnames(data), "MI04T2")]
data <- data[, !str_detect(colnames(data), "fru")]
```

```{r}
# Note: metaG samples have been sequenced twice: once shallow, once deep. keep deep only
shallow <- data[, str_detect(colnames(data), "metaG") & as.numeric(str_split(colnames(data)[str_detect(colnames(data), "metaG")], "_S", simplify = TRUE)[, 2]) < 95]
data <- data[, !colnames(data) %in% colnames(shallow)]

colnames(data) <- str_split(colnames(data), "_S", simplify = TRUE)[, 1]
```



Normalization

```{r}
# Counts per million
data_cpm <- data

# data_cpm <- aggregate(data_cpm[, 5:ncol(data_cpm)], by = list(species = data_cpm$species, Name = data_cpm$Name), sum)

data_cpm[, 5:ncol(data_cpm)] <- apply(data_cpm[, 5:ncol(data_cpm)], 2, function(x) x/sum(x) * 1000000)
```



## TE calculation 

```{r, eval = TRUE}
# Create separate matrices for each omic
metaG_mat <- data_cpm[, str_detect(colnames(data_cpm), "metaG")]
colnames(metaG_mat) <- str_replace(colnames(metaG_mat), "_metaG", "")
metaT_mat <- data_cpm[, str_detect(colnames(data_cpm), "metaT")]
colnames(metaT_mat) <- str_replace(colnames(metaT_mat), "_metaT", "")
metaRS_mat <- data_cpm[, str_detect(colnames(data_cpm), "metaRS")]
colnames(metaRS_mat) <- str_replace(colnames(metaRS_mat), "_metaRS", "")

# order them the same
metaRS_mat <- metaRS_mat[, colnames(metaT_mat)]
metaG_mat <- metaG_mat[, colnames(metaT_mat)]

# Rename columns
colnames(metaG_mat) <- paste(colnames(metaT_mat), "metaG", sep = "_")
colnames(metaT_mat) <- paste(colnames(metaT_mat), "metaT", sep = "_")
colnames(metaRS_mat) <- paste(colnames(metaRS_mat), "metaRS", sep = "_")


metaG_mat[metaG_mat<1] <- 0
metaRS_mat[metaRS_mat<1] <- 0
metaT_mat[metaT_mat<1] <- 0


table(metaRS_mat[metaRS_mat == 0])
metaRS_mat[metaT_mat < 1] <- 0
table(metaRS_mat[metaRS_mat == 0])

TE_mat <- metaRS_mat / metaT_mat
colnames(TE_mat) <- str_replace(colnames(TE_mat), "_metaRS", "_TE")

# NaN produced when 0/0
TE_mat[is.na(TE_mat)] <- 0

# Inf produced when x/0
is.na(TE_mat) <- sapply(TE_mat, is.infinite)
TE_mat[is.na(TE_mat)] <- 0
#TE_mat[TE_mat<1] <- 0

data_cpm <- data.frame(cbind(data_cpm[, 1:4], metaG_mat, metaT_mat, metaRS_mat, TE_mat))
```



```{r, fig.width = 12, fig.height = 4}
vec_col <- c("seagreen4",
              "#2171B5",
             "darkorange2", "olivedrab3",  "midnightblue", "deeppink",
              "paleturquoise4",    "orange", "orchid3",
           "gold","dodgerblue",  "mediumpurple3", 
           "hotpink2","green3", "tomato", 
           "violetred4",  "khaki2", "darkslateblue", "turquoise3", 
           "seagreen3", 
           "grey", "black")

df_agg <- aggregate(data_cpm[, 5:ncol(data_cpm)], by = list(species = data_cpm$species), sum)
df_agg <- df_agg[, !str_detect(colnames(df_agg), "_TE")]

df_agg$average_metaG <- apply(df_agg[, str_detect(colnames(df_agg), "MI04")], 1, mean)
df_agg <- df_agg[order(df_agg$average_metaG, decreasing = TRUE), ]
top20 <- df_agg$species[1:20]

df_agg$top <- ifelse(df_agg$species %in% top20, df_agg$species, "other")

# reorder alphabetically
df_agg <- df_agg[order(df_agg$species), ]
df_agg$top <- ordered(df_agg$top, levels = c(as.character(unique(df_agg$top[df_agg$top!="other"])) , "other"))

df_plots <- reshape::melt(df_agg)
colnames(df_plots) <- c("Taxon", "top", "Sample", "count")
df_plots <- df_plots[order(df_plots$Taxon), ]
df_plots <- df_plots[!str_detect(df_plots$Sample, "average"), ]
df_plots$Sample <- as.character(df_plots$Sample)

df_plots$indiv <- str_split(df_plots$Sample, "_", simplify = TRUE)[,1]
df_plots$prebiotic <- str_split(df_plots$Sample, "_", simplify = TRUE)[,2]
df_plots$replicate <- str_split(df_plots$Sample, "_", simplify = TRUE)[,3]
df_plots$omic <- str_split(df_plots$Sample, "_", simplify = TRUE)[,4]

df_plots$omic <- ordered(df_plots$omic, levels = c("metaG", "metaT", "metaRS"))


df_plots$Sample <- str_split(df_plots$Sample, "_meta", simplify = TRUE)[,1]

ggplot(df_plots, aes(fill=top, y=count, x=Sample)) +
    geom_bar(stat="identity", position = "fill") +
    scale_fill_manual(values = vec_col) +
     facet_wrap(.~ indiv + omic, ncol = 3, scales = "free") +
   theme(text = element_text(size = 15)) +
      labs(y = "Relative Abundance") +
       theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
```

# -------------------------------------------------

# KEGG-Uniref90 database annotation

```{r, eval = TRUE}
keggwol <- read.table("/home/moyne/Moyne_disk/Databases/ko_kegg_uniref_pathway_manuallycurated.tsv", 
                    sep="\t", dec=".", header = TRUE, stringsAsFactors = FALSE, na.strings = "", 
                    fill = TRUE)

table(data_cpm$uniref %in% keggwol$uniref)
keggwol <- keggwol[keggwol$uniref %in% data_cpm$uniref, ]  # keep only relevant
```

I manually curated (roughly) a database that maps all Uniref protein IDs to KEGG pathways. This allows to get more detailed pathway information than what is in the WoL database. 

```{r}
keggs <- read.table("/home/moyne/Moyne_disk/Databases/kegg/kegg_classification_grouped_by_CAT_PATH_format8.csv", 
                    sep=c(";", ","), dec=".", header = TRUE, stringsAsFactors = FALSE, na.strings = "", quote = "", 
                    fill = TRUE)

keggs[!str_detect(keggs$kegg, "K0")  & !str_detect(keggs$kegg, "K1") & !str_detect(keggs$kegg, "K2") & !str_detect(keggs$kegg, "M0"), ]

genes_KEGG <- merge(keggwol, keggs, by = "kegg", all = TRUE)

genes_KEGG <- genes_KEGG[!is.na(genes_KEGG$uniref), ]

table(is.na(genes_KEGG$pathway.x))
table(is.na(genes_KEGG$subcategory))

# Examples deeper annotation:
table(genes_KEGG[genes_KEGG$uniref == "Q32BA3", ]$pathway.x, genes_KEGG[genes_KEGG$uniref == "Q32BA3", ]$subcategory)
table(genes_KEGG[genes_KEGG$uniref == "Q32BA3", ]$pathway.x, genes_KEGG[genes_KEGG$uniref == "Q32BA3", ]$pathway.y)

table(genes_KEGG[genes_KEGG$uniref == "A0A1J1EII0", ]$pathway.x, genes_KEGG[genes_KEGG$uniref == "A0A1J1EII0", ]$subcategory)
table(genes_KEGG[genes_KEGG$uniref == "A0A1J1EII0", ]$pathway.x, genes_KEGG[genes_KEGG$uniref == "A0A1J1EII0", ]$pathway.y)
```



## Merge count table with KEGG annotation 

```{r}
datakegg_wol <- merge(keggwol, data_cpm, by = "uniref", all.y = TRUE)
datakegg <- merge(genes_KEGG, data_cpm, by.x = "uniref", by.y = "uniref", all.y = TRUE)

datakegg_wol[!is.na(datakegg_wol$kegg), ]
datakegg[!is.na(datakegg$kegg), ]

table(datakegg_wol[!is.na(datakegg_wol$kegg), ]$species)
table(datakegg[!is.na(datakegg$kegg), ]$species)

### Instruction
### 1) find out the % of genes that get a kegg annotation
nrow(datakegg_wol[!is.na(datakegg_wol$kegg), ]) / nrow(datakegg_wol) * 100 # 32%
nrow(datakegg[!is.na(datakegg$kegg), ]) / nrow(datakegg) * 100 # 45%

### 2) what proportion of the total counts for each -omic does it represent?
sum(datakegg_wol[!is.na(datakegg_wol$kegg), str_detect(colnames(datakegg_wol), "MI04")]) / sum(datakegg_wol[, str_detect(colnames(datakegg_wol), "MI04")]) * 100 # 39%
sum(datakegg[!is.na(datakegg$kegg), str_detect(colnames(datakegg), "MI04")]) / sum(datakegg[, str_detect(colnames(datakegg), "MI04")]) * 100 # 52%
```

Annotation with datakegg looks more complete and more detailed than datakegg_wol. 



### Aggregate

```{r, fig.height=4, eval = TRUE}
datakegg <- datakegg[!is.na(datakegg$kegg), ]
datakegg_agg <- datakegg[!is.na(datakegg$pathway.y), ]
# datakegg_agg$species <- str_split(datakegg_agg$species, " ", simplify = TRUE)[, 1] # genus level 

datakegg_agg1 <- aggregate(datakegg_agg[, str_detect(colnames(datakegg_agg), "meta")], by = list(datakegg_agg$species, datakegg_agg$pathway.y), sum)
datakegg_agg2 <- aggregate(datakegg_agg[, str_detect(colnames(datakegg_agg), "TE")], by = list(datakegg_agg$species, datakegg_agg$pathway.y), sum)

datakegg_agg <- data.frame(cbind(datakegg_agg1, datakegg_agg2[, 3:ncol(datakegg_agg2)]))

colnames(datakegg_agg) <- c("species", "pathway", colnames(datakegg_agg)[3:ncol(datakegg_agg)])
datakegg_agg$pathway <- str_split(datakegg_agg$pathway, " \\[PATH", simplify = TRUE)[, 1]
```




# Microbial Interactions (MI) predictions

- Average replicate
- Make table with rows = bacteria, columns = pathways
- PCA
- HCPC (Hierarchical clustering on the principal components): creates guilds of bacteria that prioritize the same pathways


## TE

```{r}
TE_BHI <- datakegg_agg[, !str_detect(colnames(datakegg_agg), "metaG") & !str_detect(colnames(datakegg_agg), "metaT") & !str_detect(colnames(datakegg_agg), "metaRS")]

# TE_BHI <- TE_BHI[TE_BHI$species %in% top30, ]

rownames(TE_BHI) <- paste(TE_BHI[, 1], TE_BHI[, 2], sep = "|")
TE_pca <- TE_BHI[, str_detect(colnames(TE_BHI), "MI04T1_ref")]


TE_pca <- apply(TE_pca, 1, mean)


TE_pca <- data.frame(cbind(TE_BHI[, c("species", "pathway")], TE = TE_pca))

TE_pca <- reshape(TE_pca,
        direction = "wide", 
        idvar = "species", 
        timevar = "pathway")

TE_pca[is.na(TE_pca)] <- 0

rownames(TE_pca) <- TE_pca$species
TE_pca <- TE_pca[, !colnames(TE_pca) == "species"]

sort(apply(TE_pca, 1, sum))
quantile(apply(TE_pca, 1, sum), seq(0,1,0.1))

TE_pca <- TE_pca[apply(TE_pca, 1, sum)>0, ]

sort(apply(TE_pca, 1, sum))
quantile(apply(TE_pca, 1, sum), seq(0,1,0.1))

TE_pca <- TE_pca[apply(TE_pca, 1, sum)>25, ] # good filters for TE
TE_pca <- TE_pca[, apply(TE_pca, 2, sum)>1]


colnames(TE_pca) <- gsub("TE.", "", colnames(TE_pca))
colnames(TE_pca) <- str_split(colnames(TE_pca), "\\[", simplify = TRUE)[,1]

summary(TE_pca[TE_pca>0])
```

PCA

```{r,  fig.height=4.5, fig.width=6.5}
pca <- PCA(log(TE_pca + 0.01), 
           scale.unit = FALSE, 
           graph = TRUE, 
           ncp = 5
           )

var_explained <- data.frame(pca$eig)
var_explained$PC <- rownames(var_explained)
var_explained$PC <- ordered(var_explained$PC, levels = unique(var_explained$PC))

ggplot(var_explained, aes(x = PC, y = percentage.of.variance)) +
  geom_bar(stat = "identity") +
    geom_vline(xintercept = 5.5, col = "red")
```


```{r,  fig.height=4.5, fig.width=6}
fviz_pca_ind(pca,
             geom = c("point", "text"), 
             repel = TRUE
             )
```


```{r, fig.width = 10, fig.height = 6}
tree <- hclust(dist(pca$ind$coord, method = "euclidean"), method = "ward.D2")
cutree(tree, k = 6)
plot(x = tree, labels =  row.names(tree), cex = 1, hang = -1, font = 3)
# 
# setwd("/home/moyne/Moyne_disk/MOMI_2020/MI04_prebiotics_test/multiomics_batch2_BHI/WoL_subset")
# svg("guilds_TE_MI04T1_BHI_WolSubbset_5PCs.svg", height = 5, width = 6)
# plot(x = tree, labels =  row.names(tree), cex = 1, hang = -1, font = 3)
# dev.off()
```



### Predicting competition: Distance matrix analysis

```{r, fig.height=8, fig.width=10}
hclustfunc <- function(x) hclust(x, method="ward.D2") # clustering ward
distfunc <- function(x) dist(x, method="euclidean")   # distances euclidiennes 

distmat <- as.data.frame(as.matrix(dist(pca$ind$coord, method = "euclidean")))
distmat[distmat == 0] <- NA

heatmap.2(as.matrix(distmat),
          trace = "none",
          #Rowv = FALSE,
          #Colv = FALSE,
          hclustfun = hclustfunc, 
          margins = c(10,10),
          col=redblue,
          scale = "none",
          na.color = "black"
)

# setwd("/home/moyne/Moyne_disk/MOMI_2020/MI04_prebiotics_test/multiomics_batch2_BHI/WoL_subset/")
# svg("Guilds_Dist_Heatmap_rowscaled_MI04T1.svg")

heatmap.2(as.matrix(distmat),
          trace = "none",
          #Rowv = FALSE,
          #Colv = FALSE,
          hclustfun = hclustfunc, 
          margins = c(10,10),
          col=redblue,
          scale = "row",
          na.color = "black"
)
# dev.off()
```

## SCORE

```{r, fig.height=7, fig.width=7}
# -(Z-score of distances)
score <- data.frame(t(apply(distmat, 1, function(x) - (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE))))

apply(score, 1, summary)
score
```


```{r, fig.height=10, fig.width=10}

cool = rainbow(50, start=rgb2hsv(col2rgb('cyan'))[1], end=rgb2hsv(col2rgb('blue'))[1])
warm = rainbow(50, start=rgb2hsv(col2rgb('red'))[1], end=rgb2hsv(col2rgb('yellow'))[1])
cols = c(rev(cool), rep("white", 3), rev(warm))
mypalette <- colorRampPalette(cols)(21)


  # setwd("/home/moyne/Moyne_disk/Soil_project/Final_datasets/REAL_SOIL_SAMPLES/Figures_final")
  # svg("competition_scores_SynCominSoil2.svg")
heatmap.2(as.matrix(score), 
          trace = "none", 
          # Rowv = FALSE,
          # Colv = FALSE, 
          margins = c(10,10), 
         col = mypalette, 
          labCol=as.expression(lapply(colnames(score), function(a) bquote(italic(.(a))))),
          labRow=as.expression(lapply(rownames(score), function(a) bquote(italic(.(a))))),
         scale = "none", 
         na.color = "black", 
         key.xlab = "Competition Score", 
         lhei = c(1,3.5), lwid = c(1,3.5), 
         density.info = "none"
)
 # dev.off()

```


```{r}
# Create an empty list to store the results
compet <- list()

# Iterate over each row of the "score" matrix
for (i in 1:nrow(score)) {
  row_name <- rownames(score)[i]
  
  # Extract column names for the current row and sort in decreasing order
  ZZZZZ_compet <- colnames(sort(score[row_name, ], decreasing = TRUE))
  
  # Apply the additional transformations to the "ZZZZZ_compet" vector
  ZZZZZ_compet <- str_replace(ZZZZZ_compet, "CAG.", "CAG:")
  ZZZZZ_compet <- str_replace_all(ZZZZZ_compet, "\\.", " ")
  ZZZZZ_compet <- str_replace_all(ZZZZZ_compet, "sp ", "sp.")
  ZZZZZ_compet <- ZZZZZ_compet[!str_detect(ZZZZZ_compet, str_split(rownames(score)[i], "\\ ", simplify = TRUE)[, 1])][1:10] #top10

  # Store the result in the list
  compet[[row_name]] <- ZZZZZ_compet
}

# Access the results for each row by row name
# Example: compet[["ZZZZ"]]

compet

#------
sort(score["Enterococcus faecium", ], decreasing = TRUE)
sort(score["Bifidobacterium longum", ], decreasing = TRUE)
sort(score["Lactobacillus", ], decreasing = TRUE)
sort(score["Collinsella", ], decreasing = TRUE)

sort(score["Bacteroides", ], decreasing = TRUE)
sort(score["Sellimonas", ], decreasing = TRUE)
sort(score["Clostridium", ], decreasing = TRUE)

```
